\documentclass[12pt,a4paper,twoside]{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[pdftex]{graphicx}      	%%% graphics for pdfLaTeX
\DeclareGraphicsExtensions{.pdf}   	%%% standard extension for included graphics
\usepackage{rotating}    				%%% causes an error if inserted in front of
												%%% DeclareGraphicsExtension
\usepackage{lscape}
\usepackage{amsfonts}
\usepackage{colordvi}
%\usepackage[pdftex]{thumbpdf}      %%% thumbnails for pdflatex
\usepackage[pdftex,                	%%% hyper-references for pdflatex
bookmarks=true,%                   	%%% generate bookmarks ...
bookmarksnumbered=true,%           	%%% ... with numbers
hypertexnames=false,%              	%%% needed for correct links to figures !!!
breaklinks=true,%                  	%%% break links if exceeding a single line
bookmarks=true,
bookmarksnumbered=false,
colorlinks=true,
pdfstartview=FitH,                 	%%% possible value Fit, FitB, FitH
linktocpage=true,
linkbordercolor={0 0 1}]{hyperref} 	%%% blue frames around links
%                                  	%%% pdfborder={0 0 1} is the default
\hypersetup{
pdfauthor   = {Reinhard Jansohn},
pdftitle    = {pythonOCC },
pdfsubject  = {pythonOCC },
pdfkeywords = {pythonOCC },
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Parts of the text may be set multi column
\usepackage{multicol}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Caution: There are difficulties reported if subfigue is used with pdflatex 
% Search the web if problems arise
\usepackage{subfigure}
% A little bit more space between the subfigure title und the figure and the 
% annotation
\addtolength{\subfigcapskip}{0.5cm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Layout of titles
\usepackage{caption}
\captionsetup{format=hang,margin=10pt,font=small,labelfont=bf}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% empahsized equations
\usepackage{empheq}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Umlauts, german stuff Degree sign and so on 
\usepackage[ansinew]{inputenc}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Fonts
\usepackage[T1]{fontenc}
\newcommand{\changefont}[3]{
\fontfamily{#1} \fontseries{#2} \fontshape{#3} \selectfont}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Length and distances
%
\unitlength1.0cm
\renewcommand{\baselinestretch}{1.15}              % distance between lines
\setlength{\parskip}{0.7ex plus 0.2ex minus 0.4ex} % distance between paragraphs
% some adaptions
\setlength{\oddsidemargin}{-0.3cm}
\setlength{\evensidemargin}{-0.3cm}
\setlength{\textwidth}{16.8cm}
\setlength{\textheight}{23.0cm}
\setlength{\topmargin}{-2.0cm}
\addtolength{\headheight}{1.0cm}
% sample
%
%\newlength{\somewidth}
%\setlength{\somewidth}{13.5cm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% graphics for pdfLaTeX
\usepackage[pdftex]{graphicx}     
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{fancybox}      
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{color}
\definecolor{Blau}{rgb}{0.1,0.1,1.0}
\definecolor{Schwarz}{rgb}{0,0,0}
\definecolor{Grau}{rgb}{0.5,0.5,0.5}
\definecolor{DunkelGrau}{rgb}{0.15,0.15,0.15}
\definecolor{Hellbraun}{rgb}{0.5,0.25,0.0}
\definecolor{Magenta}{rgb}{1.0,0.0,1.0}
\definecolor{gray}{gray}{0.5}
\definecolor{green}{rgb}{0,0.5,0}
\definecolor{SourceHintergrund}{rgb}{1,1.0,0.95}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Python sources
\usepackage{listings}
\usepackage{textcomp}
\usepackage{setspace}
\usepackage{palatino}
%
\renewcommand{\lstlistlistingname}{Code Listings}
\renewcommand{\lstlistingname}{Code Listing}

\lstnewenvironment{python}[1][]{
\lstset{
language=python,
basicstyle=\ttfamily\footnotesize\setstretch{1}, 	% print whole listing 
																	% footnotesize
stringstyle=\color{red},                    			% type for strings
showstringspaces=false,                     			% no special string spaces
alsoletter={1234567890},
otherkeywords={\ , \}, \{},
keywordstyle=\color{blue},
emph={access,and,break,class,continue,def,del,elif ,else,%
except,exec,finally,for,from,global,if,import,in,i s,%
lambda,not,or,pass,print,raise,return,try,while},
emphstyle=\color{black}\bfseries,
emph={[2]True, False, None, self},
emphstyle=[2]\color{green},
emph={[3]from, import, as},
emphstyle=[3]\color{blue},
upquote=true,
morecomment=[s]{"""}{"""},
commentstyle=\color{Hellbraun}\slshape,    			% type for comments  
emph={[4]1, 2, 3, 4, 5, 6, 7, 8, 9, 0},
emphstyle=[4]\color{blue},
literate=*{:}{{\textcolor{blue}:}}{1}%
{=}{{\textcolor{blue}=}}{1}%
{-}{{\textcolor{blue}-}}{1}%
{+}{{\textcolor{blue}+}}{1}%
{*}{{\textcolor{blue}*}}{1}%
{!}{{\textcolor{blue}!}}{1}%
{(}{{\textcolor{blue}(}}{1}%
{)}{{\textcolor{blue})}}{1}%
{[}{{\textcolor{blue}[}}{1}%
{]}{{\textcolor{blue}]}}{1}%
{<}{{\textcolor{blue}<}}{1}%
{>}{{\textcolor{blue}>}}{1},%
%framexleftmargin=1mm, framextopmargin=1mm, frame=shadowbox, rulesepcolor=\color{blue},#1
backgroundcolor=\color{SourceHintergrund}, 
framexleftmargin=1mm, framexrightmargin=1mm, framextopmargin=1mm, frame=single, framerule=1pt, rulecolor=\color{Schwarz},#1
}}{}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% numbering
\setcounter{secnumdepth}{5}
\setcounter{tocdepth}{4}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% document
%
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{titlepage}
\begin{center}
{
\large 
Geometry Modeling And Visualisation 

\vspace*{0.3cm}
Using SciPy And pythonOCC
}

{

\vspace*{0.75cm}
Reinhard Jansohn

\vspace{0.5cm}
\today
}
\end{center}
{

\vspace*{0.75cm}
{\small
\begin{center}
{\bf Abstract}
\end{center}
The results of computations in 3D cannot be drawn easily on a two dimensional medium like paper.
As a consequence mathematical books and introductional texts dealing with that often do not offer many figures which help students gaining an imagination of the meaning of all the formulas.
The remedy is the application of a mathematical software combined with the visualization capabilities of a 3D modelling software.
Python~\cite{PYTHON_ORG} offers both maths (Scipy~\cite{SCIPY_ORG}) and visualization capabilities (pythonOCC~\cite{PYTHONOCC_ORG}). 
In addition Python may be learned in a few days.
This document shows how to visualise geometric computations performed with SciPy in pythonOCC.

For SciPy the documentation and other sources on the web provide a huge amount of information.
But how to create visualizations with the aid of pythonOCC? 
Looking for information about that will give you less extensive documents\footnote{This is only true for the actual version 0.4 of pythonOCC at time of writing.}.
This little paper may help you to get started creating visualizations utilising pythonOCC more painlessly.

After reading and trying the step by step examples you should be able to write your code simply by steeling snippets from the examples delivered with pythonOCC.

\begin{center}
{\bf Acknowledgement}
\end{center}
This little booklet would not exist without the support of Thomas Paviot. I also like to thank all developers of Open~Cascade and pythonOCC for their great work.
}
}
\end{titlepage}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\include{license}
\tableofcontents
\include{Step1}
\include{Step2}
\include{Step3}
\include{Step4}
%\include{Step5}
\appendix
\include{References}
\include{Appendix_wx_PySimpleApp}
\include{History}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
